Every Author as First Author

### 2023-03-29 paper.tex
Tooltip screenshots

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

Of course, we want to give authors (equal) credit for their papers,
not remove all credit.
We have implemented two ways to reveal the actual names present in a stack.

First, hovering over the stacked names should pop up a tooltip with the
authors listed in their original order.
%In practice, PDF viewers do not seem to display the tooltips for text that is
%also a link to the bibliography, so readers must click on the link and then
%hover over the name stack in the bibliography; hopefully this extra step
%will be unnecessary in the future.
This feature works on all desktop PDF viewers we have tested,
except Chrome%
\footnote{See \url{https://bugs.chromium.org/p/chromium/issues/detail?id=1122489}}%
, but does not work on mobile devices we tested
(probably because they lack a natural notion of ``hovering'').
Because tooltips and links are both types of PDF annotations, they would
conflict with each other if used together, so we had to remove hyperlinks
from names; the years remain clickable links to the bibliography.

>>>>

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage{graphicx}
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

Of course, we want to give authors (equal) credit for their papers,
not remove all credit.
We have implemented two ways to reveal the actual names present in a stack,
when viewing a PDF file on a computer.

First, hovering over the stacked names should pop up a tooltip with the
authors listed in their original order, as shown in
Figure~\ref{fig:tooltip}.
%In practice, PDF viewers do not seem to display the tooltips for text that is
%also a link to the bibliography, so readers must click on the link and then
%hover over the name stack in the bibliography; hopefully this extra step
%will be unnecessary in the future.
This feature works on all desktop PDF viewers we have tested,
except Chrome%
\footnote{See \url{https://bugs.chromium.org/p/chromium/issues/detail?id=1122489}}%
, but does not work on mobile devices we tested
(probably because they lack a natural notion of ``hovering'').
Because tooltips and links are both types of PDF annotations, they would
conflict with each other if used together, so we had to remove hyperlinks
from names; the years remain clickable links to the bibliography.

\begin{figure}[htbp]
  \centering
  \hrule

  \includegraphics[scale=0.5]{figs/tooltip-text.png}

  \hrule

  \includegraphics[scale=0.5]{figs/tooltip-bib.png}
  \caption{Hovering over a name stack reveals the authors in their original
    order, as they would normally be written in the citation (above)
    or bibliography (below).  Screenshots from
    Visual Studio Code LaTeX Workshop Extension's internal PDF viewer,
    which is based on PDF.js.}
    % https://github.com/James-Yu/LaTeX-Workshop/wiki/View
  \label{fig:tooltip}
\end{figure}
